Probabilistic Catalogs for Crowded Stellar Fields

### 2012-11-08 paper/ms.tex
DFM before Hogg in author order
discussion section notes

\section{Conclusions}
We can do it. This is important because...

>>>>

\section{Discussion}

What have we achieved?

What are the limitations of what we have done?  Limitations include
PSF knowledge (and simplicity), simple number--flux relationship, no
astrophysical model.  On the latter, I mean: No model of temperatures,
masses, distances, reddening and so on.  We also haven't thought about
multi-epoch, multi-band imaging, where you have to consider the
motions and variations and spectral energy distributions of stars.  On
this latter point, we should cite Lang et al (faint motion).  Each of
these limitations should get its own paragraph, really.

What kinds of new science will this enable?  One example would be IMF
inference in dense stellar clusters.  Another could be modeling of
distant galaxies in terms of their stellar components.  Most
importantly, astrophysics can proceed without taking the hard,
information-lossy step of fixing a catalog, somewhere between the raw
data and the science of interest!
